---
title: "Data Wrangling and Husbandry Final Project Report"
date: "29th April 2020"
output:
  html_document: 
    theme: journal
    highlight: espresso
  pdf_document: 
    theme: journal
    highlight: espresso
---

# Data Wrangling and Husbandry (Stat 597)

# Final Project Report

**By: Aayush Mandhyan (am2447)**

## Abstract
To explore and mine hidden patterns within beer datasets (brewery, beer, beer review) and
answer questions which come into mind when one thinks about a variety of beers.


## Introduction
Covid-19 The first dataset which comes into one’s mind in today’s time, is very important
but we are already looking at its analysis on the news like 10 times a day. Which made me
think in the opposite direction and seek datasets which can be challenging as well as fun at
the same time to display my skills gained in R.

It reminded me of last year’s spring break, me and my friends took a road trip South.
Towards Virginia, North Carolina to enjoy the best nature had to offer i.e. “The Smoky
Mountains”. And taste different varieties of beer we could come across. During this trip we
would stop to seek out famous local breweries and try different varieties of beer they had
to offer. The process would always be to seek out breweries, in the area we were in, via the
internet or through recommendation by locals; and learn about their types of beers, ratings
and so on before visiting the place out. Now thinking back to those times I wanted to take a
data Scientist approach to the same questions and seek answers using the below data
sources.


## Data Source
- https://www.kaggle.com/nickhould/craft-cans#beers.csv (beers, breweries)
- https://data.world/socialmediadata/beeradvocate (beer_ratings)


### Data Preprocessing 

**Loading the required packages**
```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(magrittr)
library(tibble)
library(stringr)
library(knitr)
library(broom)
library(choroplethr)
library(choroplethrMaps)
```


**Loading the dataset**
```{r}
reviews <- read.csv("D:/Classes/Spring 2020/Stat597/Final Project/dataset/beer_reviews.csv")
beers <- read.csv("D:/Classes/Spring 2020/Stat597/Final Project/dataset/beers.csv")
breweries <- read.csv("D:/Classes/Spring 2020/Stat597/Final Project/dataset/breweries.csv")
```


Let's take a look at the column information of the dataset:

**Beer dataset**

- abv: The alcoholic content by volume with 0 being no alcohol and 1 being pure alcohol
- ibu: International bittering units, which describe how bitter a drink is
- name: The name of the beer
- style: Beer style (lager, ale, IPA, etc.)
- brewery_id: Unique identifier for brewery that produces this beer
- ounces: Size of beer in ounces


**Breweries dataset**

- brewery_id: Unique identifier for brewery that produces this beer
- name: Name of the brewery
- city: City that the brewery is located in
- state: State that the brewery is located in


**Review dataset**

- brewery_id: Unique identifier for brewery that produces this beer	
- brewery_name: Name of the brewery	
- review_time: Timestamp of the review	
- review_overall: Aggregated review score	
- review_aroma: Score for beer aroma
- review_appearance: Score for beer appearance	
- review_profilename: Reviewer Profile Name	
- beer_style: Beer style (lager, ale, IPA, etc.)	
- review_palate	Score for beer palate
- review_taste: Score for beer taste	
- beer_name: The name of the beer
- beer_abv: The alcoholic content by volume with 0 being no alcohol and 1 being pure alcohol	
- beer_beerid: Unique identifier for the beer



First 2 dataset are from a single source and have same brewery_id, where as review dataset 
is sources from a different source hence has a different id for brewries. 
We need a normalized dataset consisting of all the meta data for every beer type available,
for further exploratory data analysis.




**Normalizing the dataset**

To create a Normalized data set, first we take beer and brewery dataset into consideration as they
come from a single source and have same id representation of breweries. So we inner join the first 
two dataset on brewery_id, as shown below:

```{r}
beers_breweries <- beers %>% select(-X, -id) %>% inner_join(breweries, by = c('brewery_id' = 'X'))
beers_breweries <- beers_breweries %>% rename(beer = name.x, brewery = name.y)
head(beers_breweries)
```

After the first two datasets have been merged we have to encorporate review dataset. This review dataset
has a different source, thus it has different id representation for breweries. So in this case we can not
use brewery_id to join these two datasets. But on looking closer at the data, we see that the brewery name
remains the same which we can leverage to merge these two datasets. That's what we do in the next step.

```{r}
beer_df <- reviews %>% inner_join(beers_breweries, by = c('beer_name' = 'beer'))
head(beer_df)
```

We can observe that in the resulting dataset above consists of duplicate and non-essential features.
So, next step is to keep the ones which are relevant to the premise of our analysis.

Thus, we only keep the following columns:

- beer_name: The name of the beer
- style: Beer style (lager, ale, IPA, etc.)
- abv: The alcoholic content by volume with 0 being no alcohol and 1 being pure alcohol
- ounces: Size of beer in ounces
- brewery_name: Name of the brewery	
- city: City that the brewery is located in
- state: State that the brewery is located in
- review_overall: Aggregated review score	
- review_appearance: Score for beer appearance
- review_taste: Score for beer taste
- review_aroma: Score for beer aroma
- review_palate	Score for beer palate

```{r}
beer_df <- beer_df %>% select(beer_name, style, abv, ounces, brewery_name, city, state, review_overall, review_appearance, review_taste, review_aroma, review_palate)
head(beer_df)
```

We, now have our final dataset ready to be cleaned.




**Cleaning the dataset**

Before we start analyzing our dataset, we need to make sure that the data set is void 
of any impurity i.e. NaN values.

```{r}
map_df(beer_df, ~ sum(is.na(.)))
nrow(beer_df)
beer_df <- beer_df %>% drop_na()
```

We observe that out of 98947 rows we have NaN's in 377 rows of abv column only. This we can clean up
by just removing these rows without having a significant impact on our dataset.




### Exploratory Data Analysis

Till, now we worked on merging our dataset, cleaning it for the purpose of analyzing it and finding 
actionable and valuable insights out of it. In this section we will be doing just that, and will try 
to answer some of the pertaining question which pop into ones mind when the think about beer.


**Review Summary**

First off let us take a look at various statistics of the review scores. These gives us insights into
the distribution of scores for each criteria for a beer such:

- Appearance: How does the beer look, its color, its thickness, etc> This characteristics is the first 
              thing a person observes about a beer.
- Aroma: The aroma of the beer. After appearance people smell the beer once they have openned the bottle.
         If its aroma is bad no one will consume it.
- Taste: Its the most important thing about a beer. Once people have gotten over the first two characteristics 
         of the beer they want to taste it.
- Palate: This characteristic includes taste, aroma and over all texture of a beer. Which defines it in overall sense.
- Overall: Average score of the above individual characteristics.

```{r}
cat('Appearance Score:\n')
summary(beer_df$review_appearance)

cat('\nTaste Score: \n')
summary(beer_df$review_taste)

cat('\nAroma Score: \n')
summary(beer_df$review_aroma)

cat('\nPalate Score: \n')
summary(beer_df$review_palate)

cat('\nOverall Score: \n')
summary(beer_df$review_overall)
```

We observe that average ratings of our beers are quite high in all cateorgies, with a mean value between 3.67 - 3.85.
Which is safe to say that the beers in our data set are quite good.




**Find top 10 beer based on appearance score**

Lets take a look at top 10 beers based on their appearance, also find the brewery which produces them and the brewery's location:

```{r}
top_10_beers <- beer_df %>% group_by(beer_name) %>% summarise(avg=mean(review_appearance)) %>% arrange(desc(avg)) %>% head(10)

df_appearance <- data.frame(Beer = character(), Score = numeric(), Brewery_Name = character(), City = character(), State = character())
for (beer in top_10_beers$beer_name)
{
  brewery <- beer_df %>% filter(beer_name == beer) %>% head(1)
  score <- top_10_beers %>% filter(beer_name == beer) %>% head(1)
  df_appearance <- df_appearance %>% add_row(Beer = beer, Score = score$avg, Brewery_Name = brewery$brewery_name, City = brewery$city, State = brewery$state)
}
df_appearance
```




**Find top 10 beer based on aroma score**

Lets take a look at top 10 beers based on their aroma, also find the brewery which produces them and the brewery's location:

```{r}
top_10_beers <- beer_df %>% group_by(beer_name) %>% summarise(avg=mean(review_aroma)) %>% arrange(desc(avg)) %>% head(10)

df_aroma <- data.frame(Beer = character(), Score = numeric(), Brewery_Name = character(), City = character(), State = character())
for (beer in top_10_beers$beer_name)
{
  brewery <- beer_df %>% filter(beer_name == beer) %>% head(1)
  score <- top_10_beers %>% filter(beer_name == beer) %>% head(1)
  df_aroma <- df_aroma %>% add_row(Beer = beer, Score = score$avg, Brewery_Name = brewery$brewery_name, City = brewery$city, State = brewery$state)
}
df_aroma
```




**Find top 10 beer based on taste score**

Lets take a look at top 10 beers based on their taste, also find the brewery which produces them and the brewery's location:

```{r}
top_10_beers <- beer_df %>% group_by(beer_name) %>% summarise(avg=mean(review_taste)) %>% arrange(desc(avg)) %>% head(10)

df_taste <- data.frame(Beer = character(), Score = numeric(), Brewery_Name = character(), City = character(), State = character())
for (beer in top_10_beers$beer_name)
{
  brewery <- beer_df %>% filter(beer_name == beer) %>% head(1)
  score <- top_10_beers %>% filter(beer_name == beer) %>% head(1)
  df_taste <- df_taste %>% add_row(Beer = beer, Score = score$avg, Brewery_Name = brewery$brewery_name, City = brewery$city, State = brewery$state)
}
df_taste
```




**Find top 10 beer based on palate score**

Lets take a look at top 10 beers based on their palate, also find the brewery which produces them and the brewery's location:

```{r}
top_10_beers <- beer_df %>% group_by(beer_name) %>% summarise(avg=mean(review_palate)) %>% arrange(desc(avg)) %>% head(10)

df_palate <- data.frame(Beer = character(), Score = numeric(), Brewery_Name = character(), City = character(), State = character())
for (beer in top_10_beers$beer_name)
{
  brewery <- beer_df %>% filter(beer_name == beer) %>% head(1)
  score <- top_10_beers %>% filter(beer_name == beer) %>% head(1)
  df_palate <- df_palate %>% add_row(Beer = beer, Score = score$avg, Brewery_Name = brewery$brewery_name, City = brewery$city, State = brewery$state)
}
df_palate
```




**Find top 10 beer based on overall score**

Lets take a look at top 10 beers based on their overall score, also find the brewery which produces them and the brewery's location:

```{r}
top_10_beers <- beer_df %>% group_by(beer_name) %>% summarise(avg=mean(review_overall)) %>% arrange(desc(avg)) %>% head(10)

df_overall <- data.frame(Beer = character(), Score = numeric(), Brewery_Name = character(), City = character(), State = character())
for (beer in top_10_beers$beer_name)
{
  brewery <- beer_df %>% filter(beer_name == beer) %>% head(1)
  score <- top_10_beers %>% filter(beer_name == beer) %>% head(1)
  df_overall <- df_overall %>% add_row(Beer = beer, Score = score$avg, Brewery_Name = brewery$brewery_name, City = brewery$city, State = brewery$state)
}
df_overall
```


Now we see top 10 beers based on various characteristics. Let's see if there is any beer which has occurrence in all of them.

```{r}
df_intersect <- intersect(df_appearance$Beer, df_aroma$Beer) %>% intersect(df_taste$Beer) %>% intersect(df_palate$Beer) %>% intersect(df_overall$Beer)
df_intersect
```
We observe that none of the beer belong to all 5 top categories. While some of them overlap in most. 
Example "Bridal Veil Rye Pale Ale" is found in taste, palate and overall top beers.



We have seen beers which rank the highest in these categories, but that about the places which brew them.
Do any brewery has a higher score for a particular characteristics. Lets take a look at that.




**Find top 10 breweries based on their beer appearance score**

Lets take a look at top 10 breweries based on their beer appearance score, also find thier location:

```{r}
top_10 <- beer_df %>% group_by(brewery_name) %>% summarise(avg=mean(review_appearance)) %>% arrange(desc(avg)) %>% head(10)

df_appearance <- data.frame(Brewery_Name = character(), Score = numeric(), City = character(), State = character())
for (b in top_10$brewery_name)
{
  brewery <- beer_df %>% filter(brewery_name == b) %>% head(1)
  score <- top_10 %>% filter(brewery_name == b) %>% head(1)
  df_appearance <- df_appearance %>% add_row(Brewery_Name = brewery$brewery_name, Score = score$avg, City = brewery$city, State = brewery$state)
}
df_appearance
```




**Find top 10 breweries based on their beer aroma score**

Lets take a look at top 10 breweries based on their beer aroma score, also find thier location:

```{r}
top_10 <- beer_df %>% group_by(brewery_name) %>% summarise(avg=mean(review_aroma)) %>% arrange(desc(avg)) %>% head(10)

df_aroma <- data.frame(Brewery_Name = character(), Score = numeric(), City = character(), State = character())
for (b in top_10$brewery_name)
{
  brewery <- beer_df %>% filter(brewery_name == b) %>% head(1)
  score <- top_10 %>% filter(brewery_name == b) %>% head(1)
  df_aroma <- df_appearance %>% add_row(Brewery_Name = brewery$brewery_name, Score = score$avg, City = brewery$city, State = brewery$state)
}
df_aroma
```




**Find top 10 breweries based on their beer taste score**

Lets take a look at top 10 breweries based on their beer taste also find thier location:

```{r}
top_10 <- beer_df %>% group_by(brewery_name) %>% summarise(avg=mean(review_taste)) %>% arrange(desc(avg)) %>% head(10)

df_taste <- data.frame(Brewery_Name = character(), Score = numeric(), City = character(), State = character())
for (b in top_10$brewery_name)
{
  brewery <- beer_df %>% filter(brewery_name == b) %>% head(1)
  score <- top_10 %>% filter(brewery_name == b) %>% head(1)
  df_taste <- df_appearance %>% add_row(Brewery_Name = brewery$brewery_name, Score = score$avg, City = brewery$city, State = brewery$state)
}
df_taste
```




**Find top 10 breweries based on their beer palate score**

Lets take a look at top 10 breweries based on their beer palate score, also find thier location:

```{r}
top_10 <- beer_df %>% group_by(brewery_name) %>% summarise(avg=mean(review_palate)) %>% arrange(desc(avg)) %>% head(10)

df_palate <- data.frame(Brewery_Name = character(), Score = numeric(), City = character(), State = character())
for (b in top_10$brewery_name)
{
  brewery <- beer_df %>% filter(brewery_name == b) %>% head(1)
  score <- top_10 %>% filter(brewery_name == b) %>% head(1)
  df_palate <- df_appearance %>% add_row(Brewery_Name = brewery$brewery_name, Score = score$avg, City = brewery$city, State = brewery$state)
}
df_palate
```




**Find top 10 breweries based on their beer overall score**

Lets take a look at top 10 breweries based on their beer overall score, also find thier location:

```{r}
top_10 <- beer_df %>% group_by(brewery_name) %>% summarise(avg=mean(review_overall)) %>% arrange(desc(avg)) %>% head(10)

df_overall <- data.frame(Brewery_Name = character(), Score = numeric(), City = character(), State = character())
for (b in top_10$brewery_name)
{
  brewery <- beer_df %>% filter(brewery_name == b) %>% head(1)
  score <- top_10 %>% filter(brewery_name == b) %>% head(1)
  df_overall <- df_appearance %>% add_row(Brewery_Name = brewery$brewery_name, Score = score$avg, City = brewery$city, State = brewery$state)
}
df_overall
```


Now we see top 10 beers based on various characteristics. Let's see if there is any brewery which has occurrence in all of them.

```{r}
df_intersect <- intersect(df_appearance$Beer, df_aroma$Beer) %>% intersect(df_taste$Beer) %>% intersect(df_palate$Beer) %>% intersect(df_overall$Beer)
df_intersect
```
We observe that none of the brewery belong to all 5 top categories. 




Next, lets take a look at various beer styles based on review scores. This will give us more insight into
which style is better at which characteristics.

**Top beer styles based on appearance score**

Let's take a look at the top styles based on their apprearance score.  

```{r}
beer_df %>% 
  group_by(style) %>% # Group by the beer style
  summarise(avg=mean(review_appearance)) %>% # Count per group
  filter(avg > 4) %>% # Only the larger groups
  ggplot(aes(reorder(style, avg), avg)) + # Reorder the bars
  geom_col(fill = '#B6CDE5') + 
  theme_minimal() + 
  coord_flip() +
  ylab('Average Appearance Score') +
  xlab('Styles') +
  ggtitle('Popular Beer Styles based on Appearance Score')
```




**Top beer styles based on aroma score**

Let's take a look at the top styles based on their aroma score.  

```{r}
beer_df %>% 
  group_by(style) %>% # Group by the beer style
  summarise(avg=mean(review_aroma)) %>% # Count per group
  filter(avg > 4) %>% # Only the larger groups
  ggplot(aes(reorder(style, avg), avg)) + # Reorder the bars
  geom_col(fill = '#B6CDE5') + 
  theme_minimal() + 
  coord_flip() +
  ylab('Average Aroma Score') +
  xlab('Styles') +
  ggtitle('Popular Beer Styles based on Aroma Score')
```




**Top beer styles based on taste score**

Let's take a look at the top styles based on their taste score.  

```{r}
beer_df %>% 
  group_by(style) %>% # Group by the beer style
  summarise(avg=mean(review_taste)) %>% # Count per group
  filter(avg > 4) %>% # Only the larger groups
  ggplot(aes(reorder(style, avg), avg)) + # Reorder the bars
  geom_col(fill = '#B6CDE5') + 
  theme_minimal() + 
  coord_flip() +
  ylab('Average Taste Score') +
  xlab('Styles') +
  ggtitle('Popular Beer Styles based on Taste Score')
```




**Top beer styles based on palate score**

Let's take a look at the top styles based on their palate score.  

```{r}
beer_df %>% 
  group_by(style) %>% # Group by the beer style
  summarise(avg=mean(review_palate)) %>% # Count per group
  filter(avg > 4) %>% # Only the larger groups
  ggplot(aes(reorder(style, avg), avg)) + # Reorder the bars
  geom_col(fill = '#B6CDE5') + 
  theme_minimal() + 
  coord_flip() +
  ylab('Average Palate Score') +
  xlab('Styles') +
  ggtitle('Popular Beer Styles based on Palate Score')
```




**Top beer styles based on overall score**

Let's take a look at the top styles based on their overall score.  

```{r}
beer_df %>% 
  group_by(style) %>% # Group by the beer style
  summarise(avg=mean(review_overall)) %>% # Count per group
  filter(avg > 4) %>% # Only the larger groups
  ggplot(aes(reorder(style, avg), avg)) + # Reorder the bars
  geom_col(fill = '#B6CDE5') + 
  theme_minimal() + 
  coord_flip() +
  ylab('Average Overall Score') +
  xlab('Styles') +
  ggtitle('Popular Beer Styles based on Overall Score')
```





**Brewery density across states in the United States**

Let us take a look at the number of breweries in United States accross variou states. We see this
plotted on the United States map.

```{r, echo=FALSE}
stateFromLower <-function(x) {
  #read 52 state codes into local variable [includes DC (Washington D.C. and PR (Puerto Rico)]
  st.codes<-data.frame(
    state=as.factor(c("AK", "AL", "AR", "AZ", "CA", "CO", "CT", "DC", "DE", "FL", "GA",
                      "HI", "IA", "ID", "IL", "IN", "KS", "KY", "LA", "MA", "MD", "ME",
                      "MI", "MN", "MO", "MS",  "MT", "NC", "ND", "NE", "NH", "NJ", "NM",
                      "NV", "NY", "OH", "OK", "OR", "PA", "PR", "RI", "SC", "SD", "TN",
                      "TX", "UT", "VA", "VT", "WA", "WI", "WV", "WY")),
    full=as.factor(c("alaska","alabama","arkansas","arizona","california","colorado",
                     "connecticut","district of columbia","delaware","florida","georgia",
                     "hawaii","iowa","idaho","illinois","indiana","kansas","kentucky",
                     "louisiana","massachusetts","maryland","maine","michigan","minnesota",
                     "missouri","mississippi","montana","north carolina","north dakota",
                     "nebraska","new hampshire","new jersey","new mexico","nevada",
                     "new york","ohio","oklahoma","oregon","pennsylvania","puerto rico",
                     "rhode island","south carolina","south dakota","tennessee","texas",
                     "utah","virginia","vermont","washington","wisconsin",
                     "west virginia","wyoming"))
  )
  #create an nx1 data.frame of state codes from source column
  st.x<-data.frame(state=x)
  #match source codes with codes from 'st.codes' local variable and use to return the full state name
  refac.x<-st.codes$full[match(st.x$state,st.codes$state)]
  #return the full state names in the same order in which they appeared in the original source
  return(refac.x)
}

beer_df$state<-gsub("[[:space:]]", "", beer_df$state)
beer_df$region<-stateFromLower(beer_df$state)
```

```{r, warning=FALSE}
brewery_density <- beer_df %>% group_by(region) %>% count(brewery_name) %>% summarise(value = n())
brewery_density[is.na(brewery_density)] <- 0
names(brewery_density) = c("region", "value")
plot_brewery_density <- state_choropleth(brewery_density, title  = "Breweries across United States", legend = "Count")
require(gridExtra)
grid.arrange(plot_brewery_density, ncol=1)
```

From the above map we see that there are higher number of breweries in California, Arizona, Florida, etc.
Where as the number of breweries in central america are very low.




**Average alcohol strength of beer by state**

Next, we take a look at the strength of beers accross states.

```{r, warning=FALSE}
df <- beer_df %>% group_by(region) %>% summarise(avg = mean(abv))
df[is.na(df)] <- 0
names(df) = c("region", "value")
plot_df <- state_choropleth(df, title  = "Beer strength across United States", legend = "Average ABV.")
require(gridExtra)
grid.arrange(plot_df, ncol=1)
```

From this map we see that the alcohol content in the beer are higher in middle states of the US. Where as
from the previous map we saw that the count of breweries were low in that region. 




**Average beer overall review of beer by state**

Next, we take a look at the over all review scores of beers accross states.

```{r, warning=FALSE}
df <- beer_df %>% group_by(region) %>% summarise(avg = mean(review_overall))
df[is.na(df)] <- 0
names(df) = c("region", "value")
plot_df <- state_choropleth(df, title  = "Beer average Overall Score", legend = "Average Overall Score")
require(gridExtra)
grid.arrange(plot_df, ncol=1)
```

From the above map we observe that the states where there are more number of breweries have higher 
overall score for the beer. But we also see that the states with higher average abv for a beer 
also have a higher average overall score.




**Number of styles per state**

Finally we take a look at the number of different beer styles produced based on state in the US.

```{r, warning=FALSE}
df <- beer_df
df$style <- as.character(df$style)
df <- within(df, {no.styles<-ave(style,region,FUN=function(x) length(unique(x)))})
df <- subset(df, select=c("region","no.styles"))
df <- unique(df)
df$no.styles <- as.numeric(paste(df$no.styles))
df[is.na(df)] <- 0
names(df) = c("region", "value")
plot_df <- state_choropleth(df, title  = "Count of beer styles per state", legend = "Count")
require(gridExtra)
grid.arrange(plot_df, ncol=1)
```

And we find that CA, CO, PA, NY, MI, MT, TX have a higher count of beer styles. 




**Number of styles per city**

And at last, we take a look at the cities with the most number of beer styles.

```{r, warning=FALSE}
cities_count <- beer_df %>% 
  group_by(city) %>% # Group by city
  summarise(n_breweries = n()) %>% # Count per city
  arrange(desc(n_breweries)) %>% # Sort by count descending
  top_n(20) # Return the top 20 rows

# Calculate mean average number of breweries
avg_breweries_city <- beer_df %>%
  group_by(city) %>% 
  summarise(n = n()) %>% 
  summarise(mean = mean(n)) %>%
  `$`(mean)

ggplot(data = cities_count, aes(x = reorder(city, -n_breweries), y = n_breweries)) +
  geom_col( fill = '#03A678') + 
  geom_hline(yintercept = avg_breweries_city, color = '#FFA400', size = 1) + # add horizontal line for average number
  theme_minimal() + 
  labs(x = "City", y = "Number of breweries", title = "Number of craft beer breweries by City") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) # rotate the axis text
```





## Conclusion

In this analysis, we took a deep dive into our beer data set and found some intresting insights.
We got to explore various top beers based on their different characteristics review scores, we 
got to know which berwery produced it and in in which location. We got to know where are the top 
rated breweries located. We got to see locations of various styles of beer, beer abv and 
beer overall score on the map of United States.

All this insights can be used by the buisness user as well as by an ordinary beer drinker. To seek
different styles of beer based on different criteria. They got to know which states to look
for a particular type of brew and also how much alcohol content they can expect in their beer 
based on the state they got the beer from.




## Resource

You will find the data set and the .Rmd file for this project on my github repo ([link](https://github.com/AayushMandhyan/Data-Wrangling-Beer-Dataset)).




## References

- Professor Jason Klusowski's notes and class assignments.
- https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html
- https://www.kaggle.com/nickhould/craft-cans
- https://r4ds.had.co.nz/index.html




## Acknowledgement

I would like to thank Professor Jason Klusowski for his efforts he puts into the class as well as his guidance
in learning R by doing hand-on assignments and also in incorporating those learning into this final project. 

